Normalized expressions

### 2021-03-18 analysis/normalized.Rmd
New stats about values passed to eval

index_v <- match("V", minimized_exprs)

@@

@@

r("nb call sites unique actual value", nb_actual_values_sites)
r("call sites unique actual value percent", ratio(nb_actual_values_sites, value_minimized$n_call_sites))
r("median run sites unique actual value", median(only_actual_values$nb_runs, na.rm = TRUE))
```

@@

```{r}
med_runs <- median(val_exprs$nb_runs, na.rm = TRUE)
```

@@

>>>>

index_v <- match("V", minimized_exprs)
index_x <- match("X", minimized_exprs)

@@

is_variable <- function(l) {
  substr(l, index_x, index_x) == "T"
}

@@

r("nb call sites unique actual value", nb_actual_values_sites)
r("call sites unique actual value percent", ratio(nb_actual_values_sites, value_minimized$n_call_sites))
r("median run sites unique actual value", median(only_actual_values$nb_runs, na.rm = TRUE))
r("average run sites unique actual value", mean(only_actual_values$nb_runs, na.rm = TRUE))
r("sd run sites unique actual value", sd(only_actual_values$nb_runs, na.rm = TRUE))
```

@@

```{r}
med_runs <- median(val_exprs$nb_runs, na.rm = TRUE)
avg_runs <- mean(val_exprs$nb_runs, na.rm = TRUE)
sd_runs <- sd(val_exprs$nb_runs, na.rm = TRUE)

r("one val median runs", med_runs)
r("one val average runs", avg_runs)
r("one val sd runs", sd_runs)
```

@@

Manual inspection of the source code shows that there are actually some call sites that take actual values.
If a site is exercised by many caller sites, or by many different runs, and has only values, then we reckon it is probably a _useless_ `eval`...

```{r}
val_only <- val_exprs %>% right_join(only_actual_values, by = c("src_ref", "nb_runs"))

max_val_runs <- val_only %>% filter(nb_caller_exprs == max(nb_caller_exprs)) #it happens to also be the one with the most caller expressions

val_only %>% filter(nb_caller_exprs > 5) # those ones are likely to be useless eval
```

We now want to characterize better the sites that are passed a non-default environment. Are they also the sites that can get a value or something with a variable inside?

We compute the sites which are at least one given a `V` minimized expression. Then we look at whether they are passed teh default envir or not, and if there are variables in

```{r}
minimized_sites <- E_cano %>% semi_join(val_exprs, by="src_ref") %>% group_by(src_ref) %>% 
  summarize(has_envir = any(!is.na(envir)), has_var = any(has_var, na.rm = TRUE))

non_default_envir <- minimized_sites %>% filter(has_envir)

non_default_with_var <- minimized_sites %>% filter(has_envir, has_var)
